---
title: "Transgression Proof of Concept Analysis"
output: html_notebook
---

This notebook holds the initial analysis for Transgression Condemnation Project on the data collected by Joe et al.


## Data Description

Remember that all the tweets that were not retweets had 0 favoritesCount and retweetCount. So we decided to limit this analysis to retweets only (RT)


Description                   | Count
-------------                 | -------------
All Tweets                    | 14,798,103
Tweets                        | 4,683,905
Retweet (RT)                      | 10,114,198
Condemnation RT (CRT)               | 5,665,504
Valid Time (VT) + CRT                    | 3,126,598
Severity Rating (SR) + VT + CRT   | 3,072,275

We will work on the set of SR+VT+CRT (n= 3,072,275). If we want to take political ideology into account more filtering has to be done. For each retweet we have two users. The user that has written the original tweet (RT_user_id) and the user that has retweeted the original tweet (user_id). Recall that for political ideology estimation we need the users to follow some political accounts. Here I've se the threshold to users following only one political account. Remember that as of now I don't have data only for  460 political accounts (out of the 613)

Description                   | Count
-------------                 | -------------
Unique user_ids in SR + VT + CRT                     | 776,698
Unique user_ids in SR + VT + CRT who follow at least one political account (from 460) | 210,872
retweets in SR+VT+CRT from user_ids who follow at least one political account | 1,299,095
Unique RT_user_ids in SR + VT + CRT                     | 73,573
Unique RT_user_ids in SR + VT + CRT who follow at least one political account (from 460) | 24,003
retweets in SR+VT+CRT from user_ids who follow at least one political account | 1,753,565



```{r loading data and libraries }
twitter_file = "../data/jason_condemnation_tweets.csv"
user_id_ideology_file = "../Ideology/new-jason-ideologies.rdata"
#RT_user_id_ideology_file = "../data/RT_user_id_political_ideologies.rdata"

library(ggplot2)
library(MASS)
library(dplyr)
library(glmmTMB)
library(AER)
library(pscl)
# -----------------------------loading data------------------------------
twitter_df = read.csv(twitter_file)

#load(RT_user_id_ideology_file)
#RT_user_ideologies <- res
load(user_id_ideology_file)
og_user_ideologies <- res

user_ideology_estimates = og_user_ideologies$rowcoord[,1]
user_ids = og_user_ideologies$rownames
#RT_user_ideology_estimates = RT_user_ideologies$rowcoord[,1]
#RT_user_ids = RT_user_ideologies$rownames

user_ideology_df = data.frame(user_ideology_estimates, user_ids)
#RT_user_ideology_df = data.frame(RT_user_ideology_estimates, RT_user_ids)


names(user_ideology_df)[2]<- "user_id"
twitter_df <- merge(twitter_df,user_ideology_df,by.x = "user_id")

```
```{r plot of data, fig.show="hold", out.width="50%"}

hist(twitter_df$retweet_count, main="retweet_count")

hist(twitter_df$favorite_count, main="favorite_count")

```

## Modeling FavoritesCount

### Without the political idoelogy

Since we're not using poli

```{r setting IV DV for modeling}
Y = cbind(twitter_df$favorite_count)
colnames(Y) <- c("favorite_count")    # Applying colnames
X = cbind(twitter_df$severity_prediction) 
colnames(X) <- c("Severity")    # Applying colnames
summary(Y)
summary(X)


```

```{r - zero-inflated - fav ~ sev}
#----------------------------zero inflated negative binomial----------------
zinb <- zeroinfl(Y~X | X, link="logit", dist="negbin")
summary(zinb)

```

### With the user political idoelogy

```{r setting IV DV for modeling - with politics}
Y = cbind(twitter_df$favorite_count)
colnames(Y) <- c("FavoritesCount")    # Applying colnames
X = cbind(twitter_df$severity_prediction, twitter_df$user_ideology_estimates) 
colnames(X) <- c("Severity", "UserIdeologyEstimate")    # Applying colnames
summary(Y)
summary(X)


```

```{r - zero-inflated - fav ~ sev + poli}
options(mc.cores = max(parallel::detectCores() - 1, 2L))
#memory.limit(size=32000)


#----------------------------zero inflated negative binomial----------------
zinb <- zeroinfl(Y~X | X, link="logit", dist="negbin")
summary(zinb)

```





## Modeling RetweetCount



### Without the political idoelogy

Since we're not using poli

```{r setting IV DV for modeling - RT}
Y = cbind(twitter_df$retweet_count)
colnames(Y) <- c("retweetcount")    # Applying colnames
X = cbind(twitter_df$severity_prediction) 
colnames(X) <- c("Severity")    # Applying colnames
summary(Y)
summary(X)


```



```{r - zero-inflated - RT ~ sev}
#----------------------------zero inflated negative binomial----------------
zinb <- zeroinfl(Y~X | X, link="logit", dist="negbin")
summary(zinb)

```

### With the user political idoelogy

```{r setting IV DV for modeling - with politics - RT}
Y = cbind(twitter_df$retweet_count)
colnames(Y) <- c("RetweetCount")    # Applying colnames
X = cbind(twitter_df$severity_prediction, twitter_df$user_ideology_estimates) 
colnames(X) <- c("Severity", "UserIdeologyEstimate")    # Applying colnames
summary(Y)
summary(X)


```


```{r - zero-inflated - RT ~ sev + poli}
#----------------------------zero inflated negative binomial----------------
zinb <- zeroinfl(Y~X | X, link="logit", dist="negbin")
summary(zinb)
```


